%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Advisor Data Science \& Research} % Job title
    {Municipality of Nijmegen} % Organization
    {Nijmegen, The Netherlands} % Location
    {Jan. 2014 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Analyze and model movement data from cameras and sensors to asses and improve usage of public space in the city of Nijmegen. Using forecasting and random walk models.}
      \item {Lead a team of 3 persons to modernize ongoing economic research to help colleagues and local entrepreneurs to reach their goals in overall economic growth and improve the local business climate (\underline{\href{http://nijmegen.nl/vestigingsklimaat}{nijmegen.nl/vestigingsklimaat}}). Adding natural language processing to the research arsenal}
      \item {Lead a project team of 6 persons from three governmental agencies to make and publish the regional economic monitor (\underline{\href{https://public.tableau.com/views/REM_1/Index?:embed=y&:display_count=yes&:showVizHome=no}{Regionale Economische Monitor}}). To monitor progress on economic and sustainability goals within the Arnhem and Nijmegen region. And consult with involved colleagues and politicians about the results.}
      \item {Set up a biennial research project about innovation within the municipality of Nijmegen. To monitor startup climate and to increase the retention of successful, growing businesses. Combining information from large (open) data sources, Natural Language Processing and targeted interviews with startup entrepreneurs.}
      \item {Develop a Neural Network to calibrate air quality sensor data from low cost sensors deployed by citizens within the 'Smart Emissinon' project (\underline{\href{http://smartemission.ruhosting.nl/}{smartemission.ruhosting.nl/}}).}
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {ITS \& KBA} % Organization
    {Nijmegen, The Netherlands} % Location
    {2009-2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducting interviews, gather data and analyze data. Mainly in the fields of education, housing, transport and logistics.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
